\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{hyperref}

\title{Explicit-qT: Search Log for Quantum Tanner Codes}
\author{}
\date{\today}

\begin{document}
\maketitle

\section{Purpose}
This document logs the best Quantum Tanner codes found by our search scripts.

For each group (and local-code choice), we want to record:
\begin{itemize}
  \item \textbf{Quantum code:} $(n,k)$ and best distance upper bound $d_{\mathrm{ub}}$ returned by QDistRnd, plus the number of trials / steps used.
  \item \textbf{Construction data:} the group $G$, generator multisets $A$ and $B$, and the permutations used for the local codes.
  \item \textbf{Classical slice Tanner codes:} the 4 associated classical Tanner codes (two A-slice codes and two B-slice codes), with their parameters and distance-estimation settings.
  \item \textbf{Artifacts:} paths to saved parity-check matrices for the quantum code and for the 4 classical codes.
\end{itemize}

\section{Folder convention for best-code artifacts}
All matrices + metadata for the best codes should be stored under:
\[
\texttt{best\_codes/}
\]
with one subfolder per saved code (or per ``milestone'').

Recommended structure:
\begin{itemize}
  \item \texttt{best\_codes/meta/<CODE\_TAG>.json} (all metadata: group, A/B, perms, trials, etc.)
  \item \texttt{best\_codes/matrices/<CODE\_TAG>\_HX.mtx}
  \item \texttt{best\_codes/matrices/<CODE\_TAG>\_HZ.mtx}
  \item \texttt{best\_codes/matrices/<CODE\_TAG>\_classical\_A\_H0.mtx}, etc. (4 classical matrices)
\end{itemize}

\noindent \textbf{Naming suggestion for \texttt{<CODE\_TAG>}:}\\
\texttt{G=<group>\_n=<n>\_k=<k>\_dub=<dub>\_<timestamp>\_A=<A\_id>\_B=<B\_id>}\\
(avoid spaces; keep it filesystem-friendly).

\section{Current best results recorded}

\subsection{Group $G = C_2 \times C_2 \times C_2$ (order 8), length $n=288$}
This matches the ``$n=36|G|$'' regime (e.g., local codes of length 6 on both sides), hence $n=36\cdot 8=288$.

\paragraph{Best quantum codes found so far (from the reported table).}
\begin{center}
\begin{tabular}{@{}r r l l l@{}}
\toprule
$k$ & best $d_{\mathrm{ub}}$ & when\_found(eval) & A\_id & B\_id \\
\midrule
4  & 20 & 20260121T101724Z(2745) & Ap11\_0-0-1-2-2-7 & Bp11\_0-0-1-2-4-5 \\
8  & 20 & 20260121T060647Z(769)  & Ap11\_0-0-1-2-2-6 & Bp6\_0-1-2-4-5-7 \\
12 & 17 & 20260121T034427Z(49)   & Ap11\_0-1-2-4-5-6 & Bp6\_0-1-2-3-4-7 \\
16 & 16 & 20260121T043945Z(361)  & Ap6\_0-1-2-3-4-6  & Bp6\_0-1-2-4-5-7 \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Pending details to add for each row (to be filled automatically by scripts).}
For each of the above, we still want to record:
\begin{itemize}
  \item explicit $A$ and $B$ as multisets of $G$ elements (not only the IDs),
  \item the local-code permutations: \texttt{permA}, \texttt{permB},
  \item classical slice code parameters (4 codes):
  \begin{itemize}
    \item A-slice (primal): $(H0 \otimes I; (H1 \otimes I)LA)$
    \item A-slice (dual): $(G0 \otimes I; (G1 \otimes I)LA)$
    \item B-slice (primal): $(G0' \otimes I; (G1' \otimes I)RB)$
    \item B-slice (dual): $(H0' \otimes I; (H1' \otimes I)RB)$
  \end{itemize}
  \item paths to matrices saved under \texttt{best\_codes/}.
\end{itemize}

\section{Next automation step (to implement in scripts)}
Whenever a new best quantum code is found (according to our rules):
\begin{itemize}
  \item write a JSON metadata file into \texttt{best\_codes/meta/},
  \item export all parity-check matrices (quantum HX/HZ and the 4 classical ones)
        into \texttt{best\_codes/matrices/},
  \item append (or regenerate) the corresponding TeX table entry here.
\end{itemize}


% BEGIN AUTO BEST TABLES
\section{Auto-collected best results}
This section is generated by \texttt{scripts/collect\_best\_codes.py}.
$d$ is the recorded value saved by the search pipeline (often a QDistRnd upper bound).

\subsection{Group $G = C_{2} \times C_{2} \times C_{2}$, length $n=288$}

\begin{longtable}{@{}r r r l l@{}}
\toprule
$k$ & recorded $d$ & trials & code id & source run \\
\midrule
\endhead
4 & 20 & 50000 & \texttt{C2xC2xC2\_AAp11\_0\_0\_1\_2\_2\_7\_BBp11\_0\_0\_1\_2\_4\_5\_k4\_d20} & \texttt{results/progressive\_c2xc2xc2\_d16\_20260121\_133928} \\
8 & 20 & 50000 & \texttt{C2xC2xC2\_AAp11\_0\_0\_1\_2\_2\_6\_BBp6\_0\_1\_2\_4\_5\_7\_k8\_d20} & \texttt{results/progressive\_c2xc2xc2\_d16\_20260121\_133928} \\
12 & 18 & 50000 & \texttt{C2xC2xC2\_AAp15\_0\_1\_2\_3\_4\_7\_BBp6\_0\_1\_2\_3\_4\_7\_k12\_d18} & \texttt{results/progressive\_c2xc2xc2\_d16\_20260121\_133928} \\
16 & 16 & 20000 & \texttt{C2xC2xC2\_AAp6\_0\_1\_2\_3\_4\_6\_BBp6\_0\_1\_2\_4\_5\_7\_k16\_d16} & \texttt{results/progressive\_c2xc2xc2\_d16\_20260120\_153538} \\
\bottomrule
\end{longtable}

% END AUTO BEST TABLES

\end{document}

